Proposal: DINO Methods for Style Transfer

### 2022-03-04 Proposal.tex
small wording changes

\begin{abstract}
We combine DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, with StyTr \cite{ImageStyleTransformer}, a style transferer that renders images with artistic style, and explore the nature and robustness of the resulting model.
\end{abstract}

\section{Introduction}
Style transfer is the problem of changing an image's artistic style while maintaining its ``content'', namely the object it depicts. Conventional models use a CNN to extract features from an image, take in another image indicating the desired artistic style, and attempt to apply that style to the features of the original input image. However, it has been shown that due to the locality resulting from shared weights, CNN based models struggle to capture global information of input images and suffer from feature losses \cite{ImageStyleTransformer}. To resolve these issues, models that use transformers instead of CNNs for feature and style extraction have been proposed and show better results \cite{ImageStyleTransformer}. The model StyTr proposed in \cite{ImageStyleTransformer} takes in a content image and a style image, uses two transformer encoders to capture the content and style, then renders the content with that style using a thrid transformer decoder. In our project, we will substitute the methods DINO from \cite{DINO} for the encoder components and explore the effects on the task of style transfer. The DINO method is good at extracting content even if the input images are distorted or partial, so in particular, we will implement the models and conduct experiments to explore the following questions:
\begin{enumerate}
  \item By using DINO to extract content, can we obtain a style transfer that is more robust to distortion of the content image?
  \item Does DINO's ability to capture an image's global property from local pieces give it more robustness as a style encoder?
  \item Are the results of this new style transfer method better than previous methods?
\end{enumerate}

@@

\subsection{DINO Weight Initialized Content Encoder}

>>>>

\begin{abstract}
We combine DINO \cite{DINO}, a self-supervised learning method that captures feature representations of input images, with StyTr2 \cite{ImageStyleTransformer}, a style transfer transformer that renders images with artistic style, and explore the nature and robustness of the resulting model.
\end{abstract}

\section{Introduction}
Style transfer is the problem of changing an image's artistic style while maintaining its ``content'', namely the object it depicts. Conventional models use a CNN to extract features from an image, take in another image indicating the desired artistic style, and attempt to apply that style to the features of the original input image. However, it has been shown that due to the locality resulting from shared weights, CNN based models struggle to capture global information of input images and suffer from feature losses \cite{ImageStyleTransformer}. To resolve these issues, models that use transformers instead of CNNs for feature and style extraction have been proposed and show better results \cite{ImageStyleTransformer}. The model StyTr2 proposed in \cite{ImageStyleTransformer} takes in a content image and a style image, uses two transformer encoders to capture the content and style, then renders the content with that style using a thrid transformer decoder. In our project, we will substitute the DINO method and models from \cite{DINO} for the encoder components and explore the effects on the task of style transfer. The DINO method is good at extracting content even if the input images are distorted or partial, so in particular, we will implement the models and conduct experiments to explore the following questions:
\begin{enumerate}
  \item By using DINO to extract content, can we obtain a style transfer that is more robust to distortion of the content image?
  \item Does DINO's ability to capture an image's global property from local pieces give it more robustness as a style encoder?
  \item Are the results of this new style transfer method better than previous methods?
\end{enumerate}

@@

\subsection{Initial Pretrained DINO Content Encoder}
